Working with Poisson regression

### 2021-09-24 text/21/poisson-regression.Rmd
Updated anova.md

The variables are
+ gender (fem),
+ marital status (mar),
+ number of children (kid5),
+ prestige of graduate program (phd), 
+ the number of articles published by the individual’s mentor (ment)
+ the number of articles published by the scientist (art: the outcome).

>>>>

The variables are
+ gender (fem),
+ marital status (mar),
+ number of children (kid5),
+ prestige of graduate program (phd), 
+ the number of articles published by the individual's mentor (ment)
+ the number of articles published by the scientist (art: the outcome).
